Implementation of poloidal density variation in collision operator

### 2019-02-12 doc/manual/version3/inputParameters.tex
Added stellarator asymmetric option for geometryScheme 13.

\param{boozer\_bmnc}
{2D array of reals}
{0}
{Only when \parlink{geometryScheme} == 13. }
{Fourier harmonics describing the magnetic field in Boozer coordinates,
\begin{gather}
B(\theta_B,\zeta_B) = \sum_{m,n}\mathrm{\texttt{boozer\_bmnc}}(m,n) \cos(m\theta_B-n\mathrm{\texttt{Nperiods}} \zeta_B),
\end{gather}
The first index of \texttt{ Boozer\_bmnc} corresponds to $m \in $[0,40], and the second corresponds to $n \in $[-40,40]. Here \parlink{Nperiods} can be specified in the input file.
}

>>>>

\param{boozer\_bmnc}
{2D array of reals}
{0}
{Only when \parlink{geometryScheme} == 13. }
{Fourier harmonics describing the magnetic field in Boozer coordinates,
\begin{gather}
B(\theta_B,\zeta_B) = \sum_{m,n}\mathrm{\texttt{boozer\_bmnc}}(m,n) \cos(m\theta_B-n\mathrm{\texttt{Nperiods}} \zeta_B) + \mathrm{\texttt{boozer\_bmnc}}(m,n) \sin(m\theta_B-n\mathrm{\texttt{Nperiods}} \zeta_B),
\end{gather}
The first index of \texttt{ Boozer\_bmnc} corresponds to $m \in $[0,40], and the second corresponds to $n \in $[-40,40]. Here \parlink{Nperiods} can be specified in the input file.
}

\param{boozer\_bmns}
{2D array of reals}
{0}
{Only when \parlink{geometryScheme} == 13. }
{Fourier harmonics describing the magnetic field in Boozer coordinates,
\begin{gather}
B(\theta_B,\zeta_B) = \sum_{m,n}\mathrm{\texttt{boozer\_bmnc}}(m,n) \cos(m\theta_B-n\mathrm{\texttt{Nperiods}} \zeta_B) + \mathrm{\texttt{boozer\_bmnc}}(m,n) \sin(m\theta_B-n\mathrm{\texttt{Nperiods}} \zeta_B),
\end{gather}
The first index of \texttt{ Boozer\_bmns} corresponds to $m \in $[0,40], and the second corresponds to $n \in $[-40,40]. Here \parlink{Nperiods} can be specified in the input file.
}
